On the Synchronization Power of Openflow Data Plane

### 2015-03-13 inband-STN.tex
a few typos corrected

In this section, we sketch the synchronization abstraction we build on
top of standard OpenFlow functionality. At a high level, we export a
transactional interface which allows each controller $i\in[N]$ ($N\geq
2$) to perform multiple
operations on the configuration of an OpenFlow switch as an atomic
\emph{transaction}, inspired by the concept of transactional
memory~\cite{stm-st95,tm-book}. A transaction may \emph{commit}, in
which case it appears as executed sequentially, or \emph{abort}, in
which none of its operations takes effect.

\subsection{Interface}\label{sec:t-if}
We assume that transactions may comprise operations on the flow table
of an SDN switch, such as reading flow tables or adding new rules. 
In addition we, we also assume transactional access to  two objects: a
\emph{claim-id} object, used for claiming a policy \emph{identifier} in a
given (bounded or unbounded) set, and a read-write \emph{register}
object, used for storing the current used policy identifier.
%
More precisely, a claim-id object exports operations \emph{claim} and
\emph{unclaim} and \emph{check} with the following sequential
semantics:
%The container synchronization object introduced in this paper
%is essentially a transactional memory abstraction which can be implemented
%in standard Openflow switches.
%Before presenting the technical details in the next section,%
%we give a brief overview.

@@

\item by performing $\textit{uncheck}(i)$, $i\in[N]$, controller $i$
  \emph{unchecks} identifier $k$;

@@

We assume that a register can be accessed with a
\emph{compare-and-set} (CAS) operation that takes two integer parameters
$\textit{old}$ and $\textit{new}$, reads the register and, if the
value of it is $\textit{old}$, replaces it with $\textit{new}$ and
returns $\textit{true}$; otherwise, $\textit{false}$ is returned and
we say that the CAS operation \emph{fails} (which causes an abort if
the transaction invoking it).

@@

%Note that
%, assuming such a transactional memory,  
%a $\emph{contains}(x)$ operation can be implemented as a transaction
%composed of $\textit{cond-add}(x)$ followed by $\textit{cond-delete}(x)$.  
%A \emph{set} abstraction is a special instance of a multi-set that is
%only modified with \textit{cond-add} and \textit{cond-delete}
%operations (this way the set only contains at most one copy of a given
i%tem).

>>>>

In this section, we sketch the synchronization abstraction we build on
top of the standard OpenFlow functionality. At a high level, we export a
transactional interface which allows each controller $i\in[N]$ ($N\geq
2$) to perform multiple
operations on the configuration of an OpenFlow switch as an atomic
\emph{transaction}, inspired by the transactional-memory paradigm~\cite{stm-st95,tm-book}. A transaction may \emph{commit}, in
which case it appears as executed sequentially, or \emph{abort}, in
which none of its operations takes effect.

\subsection{Interface}\label{sec:t-if}
We assume that transactions may comprise operations on the flow table
of an SDN switch, such as reading flow tables or adding new rules. 
In addition we, we also assume transactional access to  two kinds of objects: a
\emph{claim-id} object, used for claiming a policy \emph{identifier} in a
given (bounded or unbounded) set, and a read-write \emph{register}
object, used for storing the current used policy identifier.
%
A claim-id object exports operations \emph{claim},
\emph{unclaim} and \emph{check} with the following sequential
semantics:
%The container synchronization object introduced in this paper
%is essentially a transactional memory abstraction which can be implemented
%in standard Openflow switches.
%Before presenting the technical details in the next section,%
%we give a brief overview.

@@

\item by performing $\textit{unclaim}(i)$, $i\in[N]$, controller $i$
  \emph{unclaim} identifier $k$;

@@

A register can be accessed with a
\emph{compare-and-set} (CAS) operation that takes two integer parameters
$\textit{old}$ and $\textit{new}$, reads the register and, if the
value of it is $\textit{old}$, replaces it with $\textit{new}$ and
returns $\textit{true}$; otherwise, $\textit{false}$ is returned and
we say that the CAS operation \emph{fails} (which causes an abort if
the transaction invoking it).

@@

%Note that
%, assuming such a transactional memory,  
%a $\emph{contains}(x)$ operation can be implemented as a transaction
%composed of $\textit{cond-add}(x)$ followed by $\textit{cond-delete}(x)$.  
%A \emph{set} abstraction is a special instance of a multi-set that is
%only modified with \textit{cond-add} and \textit{cond-delete}
%operations (this way the set only contains at most one copy of a given
%item).
